\documentclass[10pt,a4paper,sans]{moderncv}
\usepackage[utf8]{inputenc}
\moderncvstyle{classic}
\moderncvcolor{blue}
\usepackage[scale=0.87]{geometry}
\setlength{\hintscolumnwidth}{2.5cm}
\usepackage{amsfonts,amssymb}
\usepackage{amsmath}

\firstname{Aleksey}
\familyname{Fedorov}
\address{Mitrofanova street, 23,}{Moscow Region, Lubertsy}
\phone{+7 (916) 297-09-77}
\email{lex1026@gmail.com}
\renewcommand\refname{Selected publications}
\nopagenumbers{}

\begin{document}

\begin{center}
\Large
\textcolor{blue}{CURRICULUM VITAE}
\end{center}

\section{Personal information}

	\cventry{Personal details}{Aleksey K. Fedorov}{November 1, 1993}{\textcolor{blue}{\href{http://www.rqc.ru/members/aleksey.fedorov}{RQC web-page}}}{}{}
	\cventry{RQC contacts}{\textcolor{blue}{\href{mailto:akf@rqc.ru}{akf@rqc.ru}}}
	{}{100A Novaya St.}{143025, Skolkovo, Moscow Region, Russia}{}
	\cventry{LPTMS contacts}{\textcolor{blue}{\href{mailto:aleksey.fedorov@lptms.u-psud.fr}{aleksey.fedorov@lptms.u-psud.fr}}}
	{}{100 B\^atiment, 15 rue Georges Cl{\`e}menceau}{91405, Orsay, France}{}

\section{Education}

	\cventry{Sept'15 -- \quad\dots\,\,\, \\ }
	{CNRS PhD Student}{{\textcolor{blue}{\href{https://www.universite-paris-saclay.fr/en/}{Universit{\' e} Paris-Saclay}}},
	\textcolor{blue}{\href{http://lptms.u-psud.fr/en}{Laboratoire de Physique Th{\'e}orique et Mod{\`e}les Statistique, CNRS \& Universit{\' e} Paris Sud XI}}}
	{\textit{Supervisor}: Prof. \textcolor{blue}{\href{http://staff.science.uva.nl/~walraven/shlyapnikov/GoraShlyapnikov-french.htm}{Georgy Shlyapnikov}},
	{\textit{Tutor}: Prof. \textcolor{blue}{\href{http://lptms.u-psud.fr/membres/groux/}{Guillaume Roux}}}}{}{}{}{}

	\cventry{Sept'09 -- Jun'15}
	{Master of Science (with honor)}{\textcolor{blue}{\href{http://bmstu.ru}{Bauman Moscow State Technical University --- Bauman University}}}
	{\newline Computer Science \& Control Systems}{\textit{Supervisor}: Dr. Yury Kurochkin}{}{}

\section{Research experience}

%	\cventry{Oct'15 -- \quad\dots\,\,\,}
%	{Junior Group Leader}
%	{Mathematical Institute of Russian Academy of Sciences \& \textcolor{blue}{\href{http://rqc.ru}{Russian Quantum Center}}}
%	{\textcolor{blue}{\href{http://www.rqc.ru/groups/shlyapnikov/}{Joint Quantum Information Theory Laboratory}}}{}{}	

	\cventry{Oct'12 -- \,\quad\dots\,\,\,}
	{BSc Student/RQC Student Fellow/Junior Researcher}
	{\textcolor{blue}{\href{http://rqc.ru}{Russian Quantum Center}}}
	{\textcolor{blue}{\href{http://www.rqc.ru/groups/lvovsky/}{Quantum Optics}} \& 
	\textcolor{blue}{\href{http://www.rqc.ru/groups/shlyapnikov/}{Many-body Theory}}}
	{\textit{Supervisor}: \textcolor{blue}{\href{http://www.rqc.ru/members/georgy.shlyapnikov/}{Prof. Georgy Shlyapnikov}},
	{\textit{Point of Contact}: \textcolor{blue}{\href{http://www.rqc.ru/members/alexander.lvovsky/}{Prof. Alexander Lvovsky}}}}{}
	
%	\cventry{Jul'13 -- Jun'15\,\,}
%	{RQC Student Fellow}
%	{\textcolor{blue}{\href{http://rqc.ru}{Russian Quantum Center}}}
%	{\newline \textcolor{blue}{\href{http://www.rqc.ru/groups/shlyapnikov/}{Many-body Theory}}}
%	{\textit{Supervisor}: \textcolor{blue}{\href{http://www.rqc.ru/members/georgy.shlyapnikov/}{Prof. Georgy Shlyapnikov}},
%	{\textit{Point of Contact}: \textcolor{blue}{\href{http://www.rqc.ru/members/alexander.lvovsky/}{Prof. Alexander Lvovsky}}}}{}
	
%	\cventry{Oct'12 -- Jun'13\,}
%	{BSc Student}
%	{\textcolor{blue}{\href{http://rqc.ru}{Russian Quantum Center}}}
%	{\newline \textcolor{blue}{\href{http://www.rqc.ru/groups/lvovsky/}{Quantum Optics}}}
%	{\textit{Supervisor}: \textcolor{blue}{\href{http://www.rqc.ru/members/alexander.lvovsky/}{Prof. Alexander Lvovsky}}}{}                                                        
	
	\cventry{Oct'12 -- Jul'13\,\,}
	{BSc Student}
	{\textcolor{blue}{\href{http://fn.bmstu.ru/index.php/fn4}{Department of Physics}}, \textcolor{blue}{\textcolor{blue}{\href{http://bmstu.ru}{Bauman University}}}}
	{\newline \textcolor{blue}{\href{http://teratech.ru/en}{Condensed Matter Theory}}}
	{\textit{Supervisor}: \textcolor{blue}{\href{http://teratech.ru/en/peoples}{Dr. Stanislav Yurchenko}}}{}

	\cventry{Dec'10 -- Jun'14}
	{BSc Student}
	{\textcolor{blue}{\href{http://www.ipmnet.ru}{Institute for Problem in Mechanics, Russian Academy of Sciences}}}
	{\newline \textcolor{blue}{\href{http://www.ipmnet.ru/lab02.htm}{Mechanics of Controlled Systems}}}
	{\textit{Supervisor}: \textcolor{blue}{\href{http://www.ipmnet.ru/lab02/Ovseevich.htm}{Dr. Alexander Ovseevich}}}{}
	
\section{Research visits}

	\cventry{Dec'13 -- Jan'14}
	{Visiting Scholar}
	{\textcolor{blue}{\href{http://physics.harvard.edu}{Department of Physics}}, \textcolor{blue}{\href{http://www.harvard.edu}{Harvard University}}}
	{\newline \textcolor{blue}{\href{http://cmt.harvard.edu}{Condensed Matter Theory}}}
	{\textit{Supervisor}: \textcolor{blue}{\href{http://cmt.harvard.edu/demler/}{Prof. Eugene Demler}}}{}        

	\cventry{Jul'12 -- Aug'12\,}
	{Visiting Research Associate}
	{\textcolor{blue}{\href{http://phas.ucalgary.ca}{Department of Physics and Astronomy}}, \textcolor{blue}{\href{http://www.ucalgary.ca}{University of Calgary}}}
	{\newline \textcolor{blue}{\href{http://www.iqst.ca}{Institute for Quantum Science and Technology}}}
	{\textit{Supervisor}: \textcolor{blue}{\href{http://www.rqc.ru/members/alexander.lvovsky/}{Prof. Alexander Lvovsky}}}{}	
	
\section{Professional activities}

	\cvline{Reviewing}{Elsevier Recognized Reviewer 
	(\textcolor{blue}{\href{http://www.journals.elsevier.com/physics-letters-a/}{Phys. Lett. A}}, 
	\textcolor{blue}{\href{http://www.journals.elsevier.com/annals-of-physics}{Ann. Phys.}},
	and
	\textcolor{blue}{\href{http://www.journals.elsevier.com/physica-c-superconductivity-and-its-applications/}{Phys. C}}),
	Mathematical Reviews,
	\textcolor{blue}{\href{http://pra.aps.org/}{Phys. Rev. A}}, 
	\textcolor{blue}{\href{http://iopscience.iop.org/0295-5075}{Europhys. Lett}},
	\textcolor{blue}{\href{http://www.tandfonline.com/toc/tmop20/current}{J. Modern Optics}},
	\textcolor{blue}{\href{http://link.springer.com/journal/11128}{Quant. Inf. Proc.}},
	and
	\textcolor{blue}{\href{http://omicsgroup.info/editorialtracking/theoretical/index.php}{J. Theor. Comp. Chemistry}}.}

	%\cvline{Membership}{Student membership in 
	%\textcolor{blue}{\href{http://ams.org}{AMS}}, 
	%\textcolor{blue}{\href{http://aps.org}{APS}}, 
	%and
	%\textcolor{blue}{\href{http://aps.org}{OSA}}.} 
	
	\cvline{Erd\"os number}{4}
	
\section{Fellowships and awards}

	\cvline{2015}{Award for the Best poster, ``Young Physicists Conference'', \textcolor{blue}{\href{http://www.moomfo.ru}{Moscow Physical Society}}, with E.O. Kiktenko.}

	\cvline{2015}{Scholarship for students, \textcolor{blue}{\href{http://www.its-club.ru}{Imperial Moscow Technical School Club (Alumni Club of the Bauman University)}}.}

	\cvline{2014 -- 2015}{Fellowship for students, \textcolor{blue}{\href{http://www.dynastyfdn.com/english/}{Dynasty Foundation}}.}

	\cvline{2013 -- 2015}{Fellowship for students, \textcolor{blue}{\href{http://www.rqc.ru}{Russian Quantum Center}}.}

	\cvline{2014 -- 2015}{Scholarship for students, \textcolor{blue}{\href{http://www.edu.ru/db-mon/mo/Data/d_13/m1028.html}{Russian Federation President}}.}

	\cvline{2014}{Scholarship for students, Scientific committee of the \textcolor{blue}{\href{http://www.bmstu.ru/en/}{Bauman University}}.}
	
	\cvline{2013 -- 2014}{Scholarship for students, \textcolor{blue}{\href{http://www.edu.ru/db-mon/mo/Data/d_13/m1028.html}{Russian Federation Government}}.}
	
	\cvline{2012 -- 2013}{Scholarship for students work in science, \textcolor{blue}{\href{http://www.bmstu.ru/en/}{Bauman University}}.}

	\cvline{2013}{\textcolor{blue}{\href{http://2013.infoforum.ru/novoe-pokolenie/laureaty-premii-novoe-pokolenie-v-2013-godu/}
	{``New Generation'' Award, XV National forum for information security ``INFOFORUM 2013''}}.}
	
	\cvline{2011 -- 2013}{The best conference talk, \textcolor{blue}{\href{www.phystech.edu}{Moscow Institute for Physics and Technology}}.}
	
	\cvline{2011 -- 2013}{The best student scientific work on theoretical physics, \textcolor{blue}{\href{http://www.bmstu.ru/en/}{Bauman University}}.}
	
	\cvline{2012}{Research Award for Students, \textcolor{blue}{\href{http://www.ipmnet.ru}{Institute for Problem in Mechanics RAS}}.}
	
	\cvline{2012}{Award for the Best student work on theoretical physics, {\textcolor{blue}{\href{http://www.bmstu.ru/en/}{Bauman University}}}.}
	
	\cvline{2011}{Award for the Best poster, ``Young Physicists Conference'', \textcolor{blue}{\href{http://www.moomfo.ru}{Moscow Physical Society}}.}
					
	\cvline{2009 -- 2012}{UNESCO department diploma, \textcolor{blue}{\href{http://www.bmstu.ru/en/}{Bauman University}}.}
	
	\cvline{2009}{The best scientific work in program ``Step into the Future, Moscow'', \textcolor{blue}{\href{http://www.bmstu.ru/en/}{Bauman University}}.}
	
\section{Publications in peer-reviewed journals}

	\cvline{15}
	{\textbf{A.K. Fedorov}, M.N. Anufriev, A.A. Zhirnov, K.V. Stepanov, E.T. Nesterov, D.E. Namiot, V.E. Karasik, and A.B. Pnev.
	{\textcolor{blue}{\href{http://dx.doi.org/10.1063/1.4944417}{Gaussian mixture model for events recognition in optical time-domain reflectometry based sensing systems}}} //
	Review of Scientific Instruments \textbf{87}, 036107 (2016),
	{\textcolor{blue}{\href{http://arxiv.org/abs/1509.05998}{arXiv:1509.05998}}}.}

	\cvline{14}
	{A.I. Ovseevich and \textbf{A.K. Fedorov}. 
	{\textcolor{blue}{\href{http://dx.doi.org/10.1134/S0005117915110016}{Feedback control for a system of linear oscillators}}} // 
	Automation and Remote Control \textbf{76}, 1905--1917 (2015),
	{\textcolor{blue}{\href{http://arxiv.org/abs/1509.06056}{arXiv:1509.06056}}}.}

	\cvline{13}	
	{\textbf{A.K. Fedorov}, M.N. Anufriev, A.A. Zhirnov, E.T. Nesterov, D.E. Namiot, A.B. Pnev, and V.E. Karasik 
	{\textcolor{blue}{\href{http://injoit.org/index.php/j1/article/view/232}{Towards events recognition in a distributed fiber-optic sensor system: Kolmogorov-Zurbenko filtering}}} // 
	International Journal of Open Information Technologies \textbf{3}, 16--19 (2015),
	{\textcolor{blue}{\href{http://arxiv.org/abs/1509.05996}{arXiv:1509.05996}}}.}

	\cvline{12}
	{\textbf{A.K. Fedorov} and A.I. Ovseevich. 
	{\textcolor{blue}{\href{http://dx.doi.org/10.1134/S0001434615070226}{Perturbation theory of observable linear systems}}} // 
	Mathematical Notes \textbf{98}, 216--221 (2015),
	{\textcolor{blue}{\href{http://arxiv.org/abs/1404.6901}{arXiv:1404.6901}}}.}

%	\cvline{\textcolor{blue}{11} \quad 2015}
	\cvline{11}
	{E.O. Kiktenko, \textbf{A.K. Fedorov}, A.A. Strakhov, and V.I. Man'ko. 
	{\textcolor{blue}{\href{http://dx.doi.org/10.1016/j.physleta.2015.03.023}{Single qudit realization of the Deutsch algorithm using superconducting many-level quantum circuits}}} // 
	Physics Letters A \textbf{379}, 1409--1413 (2015),
	{\textcolor{blue}{\href{http://arxiv.org/abs/1503.01583}{arXiv:1503.01583}}}.} 

%	\cvline{\textcolor{blue}{10} \quad 2015}
	\cvline{10}
	{A.I. Ovseevich  and \textbf{A.K. Fedorov}. 
	{\textcolor{blue}{\href{http://dx.doi.org/10.1134/S0005117915050082}{Motion of a system of oscillators under the generalized dry friction control}}} // 
	Automation and Remote Control \textbf{76}, 826--833 (2015),
	{\textcolor{blue}{\href{http://arxiv.org/abs/1505.00773}{arXiv:1505.00773}}}.}

%	\cvline{\textcolor{blue}{9} \quad 2015}
	\cvline{9}
	{I.A. Fedorov, \textbf{A.K. Fedorov}, Y.V. Kurochkin, and A.I. Lvovsky. 
	{\textcolor{blue}{\href{http://dx.doi.org/10.1088/1367-2630/17/4/043063}{Tomography of a multimode quantum black box}}} //
	New Journal of Physics \textbf{17}, 043063 (2015), {\textcolor{blue}{\href{http://arxiv.org/abs/1403.0432}{arXiv:1403.0432}}};
	Featured in {\textcolor{blue}{\href{http://iopscience.iop.org/article/10.1088/1367-2630/17/4/043063/meta}{IOP Select 2015}}},
	{\textcolor{blue}{\href{http://www.rqc.ru/news/?ELEMENT_ID=1195}{RQC Press Release}}}.}

%	\cvline{\textcolor{blue}{8} \quad 2015}
	\cvline{8}
	{E.O. Kiktenko, \textbf{A.K. Fedorov}, O.V. Man'ko, and V.I. Man'ko. 
	{\textcolor{blue}{\href{http://dx.doi.org/10.1103/PhysRevA.91.042312}{Multilevel superconducting circuits as two-qubit systems: Operations, state preparation, and entropic inequalities}}} //
	Physical Review A \textbf{91}, 042312 (2015),
	{\textcolor{blue}{\href{http://arxiv.org/abs/1411.0157}{arXiv:1411.0157}}}.} 

%	\cvline{\textcolor{blue}{7} \quad 2015}
	\cvline{7}
	{\textbf{A.K. Fedorov}, E.O. Kiktenko, O.V. Man'ko, and V.I. Man'ko. 
	{\textcolor{blue}{\href{http://dx.doi.org/10.1088/0031-8949/90/5/055101}{Tomographic discord for a system of two coupled nanoelectric circuits}}} //
	Physica Scripta \textbf{90}, 055101 (2015),
	{\textcolor{blue}{\href{http://arxiv.org/abs/1409.5265}{arXiv:1409.5265}}}.}

%	\cvline{\textcolor{blue}{6} \quad 2014}
	\cvline{6}	
	{\textbf{A.K. Fedorov}, I.L. Kurbakov, and Yu.E. Lozovik. 
	{\textcolor{blue}{\href{http://dx.doi.org/10.1103/PhysRevB.90.165430}{Roton-maxon spectrum and instability for weakly interacting dipolar excitons in a semiconductor layer}}} //
	Physical Review B \textbf{90}, 165430 (2014),
	{\textcolor{blue}{\href{http://arxiv.org/abs/1403.3956}{arXiv:1403.3956}}}.}
	
%	\cvline{\textcolor{blue}{5} \quad 2014}
	\cvline{5}
	{\textbf{A.K. Fedorov}, I.L. Kurbakov, Y.E. Shchadilova, and Yu.E. Lozovik.
	{\textcolor{blue}{\href{http://dx.doi.org/10.1103/PhysRevA.90.043616}{Two-dimensional Bose gas of tilted dipoles: Roton instability \& condensate depletion}}} //
	Physical Review A \textbf{90}, 043616 (2014),
	{\textcolor{blue}{\href{http://arxiv.org/abs/1407.6399}{arXiv:1407.6399}}}.}

%	\cvline{\textcolor{blue}{4} \quad 2014}
	\cvline{4}
	{E.O. Kiktenko and \textbf{A.K. Fedorov}. 
	{\textcolor{blue}{\href{http://dx.doi.org/10.1016/j.physleta.2014.04.036}{Tomographic causal analysis of two-qubit states and tomographic discord}}} //  
	Physics Letters A \textbf{378},  1704--1710 (2014), {\textcolor{blue}{\href{http://arxiv.org/abs/1309.4948}{arXiv:1309.4948}}}.}

%	\cvline{\textcolor{blue}{3} \quad 2013}
	\cvline{3}
	{\textbf{A.K. Fedorov}. 
	{\textcolor{blue}{\href{http://dx.doi.org/10.1016/j.physleta.2013.07.020}{Feynman integral and perturbation theory in quantum tomography}}} // 
	Physics Letters A \textbf{377},  2320--2323 (2013).}
	
%	\cvline{\textcolor{blue}{2} \quad 2013}
	\cvline{2}
	{\textbf{A.K. Fedorov} and E.O. Kiktenko. 
	{\textcolor{blue}{\href{http://dx.doi.org/10.1007/s10946-013-9378-z}{Quaternion representation and symplectic spin tomography}}} // 
	Journal of Russian Laser Research \textbf{34}, 477--487 (2013), 
	{\textcolor{blue}{\href{http://arxiv.org/abs/1308.6549}{arXiv:1308.6549}}}.}
	
%	\cvline{\textcolor{blue}{1} \quad 2013}
	\cvline{1}
	{A.I. Ovseevich  and \textbf{A.K. Fedorov}. 
	{\textcolor{blue}{\href{http://dx.doi.org/10.1134/S106456241305013X}{Asymptotically optimal feedback control for a system of linear oscillators}}} // 
	Doklady Mathematics \textbf{88}, 613--617 (2013).}
	
\iffalse
	
	\cvline{\textcolor{blue}{2} \quad 2013}
	{A.I. Ovseevich  and \textbf{A.K. Fedorov}. 
	{\textcolor{blue}{\href{http://www.unn.ru/eng/publications/vestnik.html?anum=6280}{Feedback bounded control for a system of oscillators}}} // 
	Vestnik of Lobachevsky State University of Nizhni Novgorod \textbf{1}, 278--283 (2013) [In Russian}.}
	
	\cvline{\textcolor{blue}{1} \quad 2012}
	{\textbf{A.K. Fedorov} and S.\,O.\,Yurchenko. 
	{\textcolor{blue}{\href{http://vestniken.bmstu.ru/eng/catalog/phys/hidden/81.html}{Symplectic tomograms presented through Feynman path integrals}}} // 
	Herald of the Bauman Moscow State Technical University \textbf{45}, 29--37 (2012) [In Russian].}
	
\fi
	
\section{Preprints}

	\cvline{2016}
	{E.O. Kiktenko, A.S. Trushechkin, Y.V. Kurochkin, and {\textbf{A.K. Fedorov}. 
	Post-processing procedure for industrial quantum key distribution systems,
	{\textcolor{blue}{\href{http://arxiv.org/abs/1603.08387}{arXiv:1603.08387}}}.}}

	\cvline{2016}
	{E.O. Kiktenko, A.A. Popov, and {\textbf{A.K. Fedorov}. 
	Bidirectional imperfect quantum teleportation with a single Bell state,
	{\textcolor{blue}{\href{http://arxiv.org/abs/1602.01420}{arXiv:1602.01420}}}.}}

	\cvline{2016}
	{{\textbf{A.K. Fedorov}, S.I. Matveenko, V.I. Yudson, and G.V. Shlyapnikov. 
	Novel $p$-wave superfluids of fermonic polar molecules,
	{\textcolor{blue}{\href{http://arxiv.org/abs/1601.03026}{arXiv:1601.03026}}}.}}

	\cvline{2015}
	{E.O. Kiktenko, {\textbf{A.K. Fedorov}, and V.I. Man'ko. 
	Teleportation in an indivisible quantum system //
	Quantum Measurements and Quantum Metrology (to be published in 2016),
	{\textcolor{blue}{\href{http://arxiv.org/abs/1512.05168}{arXiv:1512.05168}}}.}}

	\cvline{2015}
	{A.I. Ovseevich and \textbf{A.K. Fedorov}. 
	Damping of a system of linear oscillators using the generalized dry friction // 
	Proceedings of the Steklov Institute of Mathematics (to be published in 2016),
	{\textcolor{blue}{\href{http://arxiv.org/abs/1508.07775}{arXiv:1508.07775}}}.}
	
	\cvline{2013}
	{\textbf{A.K. Fedorov} and A.I. Ovseevich. 
	Asymptotic control theory for a system of linear oscillators // 
	Moscow Mathematical Journal (to be published in 2016),
	{\textcolor{blue}{\href{http://arxiv.org/abs/1308.6090}{arXiv:1308.6090}}}.}
	
\section{Conference and seminars presentations}
	
	\cvline{29/03/2016 \\ \textcolor{blue}{Poster}}
	{\textit{Post-processing procedure for the industrial quantum key distribution system}.
	\underline{E.O. Kiktenko}, A.S. Trushechkin, Y.V. Kurochkin, and \textbf{A.K. Fedorov}.
	\textcolor{blue}{\href{http://spbopen.spbau.com}{The 3rd International School and Conference ``Saint-Petersburg OPEN 2016''}}, Saint-Petersburg, Russia.}
	
	\cvline{03/02/2016 \\ \textcolor{red}{Award}}
	{\textit{Development of an industrial quantum key distributing device}.
	\underline{A.V. Duplinskiy}, A.A. Kanapin, A.V. Losev, A.S. Sokolov, E.O. Kiktenko, and \textbf{A.K. Fedorov}.
	Young Physicist Conference, Moscow, Russia
	[\textcolor{blue}{\href{http://konkmolphys.moomfo.ru/application/2015}{Physics in High Education (Special Issue) \textbf{22}, 96 (2016)}}].}

	\cvline{29/01/2016 \\ \textcolor{blue}{Talk}}
	{\textit{Superfluids of fermonic polar molecules}.
	\textbf{A.K. Fedorov}, S.I. Matveenko, V.I. Yudson, and G.V. Shlyapnikov.
	\textcolor{blue}{\href{http://comphys.ethz.ch:8080/jstat/home}{The thirty-sixth edition of the ``Journ\'{e}es de Physique Statistique''}}, Paris, France.}
	
	\cvline{18/01/2016 \\ \textcolor{blue}{Talk}}
	{\textit{Novel $p$-wave superfluids of fermonic polar molecules}.
	\textbf{A.K. Fedorov}.
	\textcolor{blue}{\href{http://lptms.u-psud.fr}{Laboratoire de Physique Th{\'e}orique et Mod{\`e}les Statistique (LPTMS) PhD Days}}, Orsay, France.}

	\cvline{21/09/2015 \\ \textcolor{blue}{Poster}}
	{\textit{Floating bases quantum key distribution protocol with decoy states}.
	\textbf{A.K. Fedorov}, V.L. Kurochkin, and Y.V. Kurochkin.
	\textcolor{blue}{\href{http://yqis15.sciencesconf.org}{International Conference for Young Quantum Information Scientists}}, Palaiseau, France.}

	\cvline{21/09/2015 \\ \textcolor{red}{Invited talk}}
	{\textit{Roton phenomena of weakly interacting dipolar excitons in a semiconductor layer}.
	\textbf{A.K. Fedorov}.
	\textcolor{blue}{\href{http://web.nano.cnr.it/CEE2D/}{Collective electronic excitations in 2D, Final conference of the INDEX project}}, Pisa, Italy.}

	\cvline{16/07/2015 \\ \textcolor{blue}{Poster}}
	{\textit{Complete characterization of multimode quantum process}.
	I.A. Fedorov, \textbf{A.K. Fedorov}, \underline{Y.V. Kurochkin}, and A. I. Lvovsky.
	\textcolor{blue}{\href{http://conference.rqc.ru}{The Third International Conference on Quantum Technologies}}, Moscow, Russia.}

	\cvline{14/07/2015 \\ \textcolor{blue}{Poster}}
	{\textit{Roton-maxon spectrum and local density waves in a two-dimensional Bose gas of dipoles}.
	\textbf{A.K. Fedorov}, I.L. Kurbakov, and Yu.E. Lozovik.
	\textcolor{blue}{\href{http://conference.rqc.ru}{The Third International Conference on Quantum Technologies}}, Moscow, Russia.}

	\cvline{14/07/2015 \\ \textcolor{blue}{Poster}}
	{\textit{Quantum key distribution protocol with floating bases and decoy states}.
	\underline{Yu.V. Kurochkin}, \textbf{A.K. Fedorov}, and V.L. Kurochkin.
	\textcolor{blue}{\href{http://conference.rqc.ru}{The Third International Conference on Quantum Technologies}}, Moscow, Russia.}
	
	\cvline{06/07/2015 \\ \textcolor{blue}{Poster}}
	{\textit{Operating with five-level superconducting circuit as a two-qubit system}.
	\underline{E.O. Kiktenko}, \textbf{A.K. Fedorov}, and V.I. Man'ko.
	\textcolor{blue}{\href{http://conference.rqc.ru}{The Third International Conference on Quantum Technologies}}, Moscow, Russia.}

	\cvline{08/07/2015 \\ \textcolor{blue}{Poster}}
	{\textit{Local stable supersolid of tilted dipoles}.
	\textbf{A.K. Fedorov}.
	\textcolor{blue}{\href{http://indico.ictp.it/event/a14248/}{Workshop on Interacting Fermions: Precision Theory and Experiment}}, Trieste, Italy.}

	\cvline{06/07/2015 \\ \textcolor{red}{Best poster}}
	{\textit{Quantum computations via multilevel superconducting circuit}.
	\underline{E.O. Kiktenko}, \textbf{A.K. Fedorov}, A.A. Strakhov, and V.I. Man'ko.
	\textcolor{blue}{\href{http://cewqo2015.fuw.edu.pl}{22nd Central European Workshop on Quantum Optics}}, Warsaw, Poland.}
	
	\cvline{06/07/2015 \\ \textcolor{blue}{Poster}}
	{\textit{Tomographic discord and information asymmetry in two-qubit $X$-states}.
	\textbf{A.K. Fedorov}, \underline{E.O. Kiktenko}, O.V. Man'ko, and V.I. Man'ko.
	\textcolor{blue}{\href{http://cewqo2015.fuw.edu.pl}{22nd Central European Workshop on Quantum Optics}}, Warsaw, Poland.}
	
	\cvline{03/03/2015 \\ \textcolor{blue}{Poster}}
	{\textit{Roton phenomena and stability properties of dipolar condensates}.
	\textbf{A.K. Fedorov}, I.L. Kurbakov, and Yu.E. Lozovik.
	\textcolor{blue}{\href{http://www.rqc.ru/events/?ELEMENT_ID=888}{APS March Meeting 2015}},
	San Antonio, Texas, USA
	[\textcolor{blue}{\href{http://dx.doi.org/10.1088/1742-6596/414/1/012036}{Bulletin of the American Physical Society}}
	\textbf{60}, 1 (2015)].}

	\cvline{03/02/2015 \\ \textcolor{red}{Best poster}}
	{\textit{Symmetric discord for two-qubit $X$-states}.
	\underline{E.O. Kiktenko} and \textbf{A.K. Fedorov},
	Young Physicist Conference, Moscow, Russia
	[\textcolor{blue}{\href{http://konkmolphys.moomfo.ru/application/2015}{Physics in High Education (Special Issue) \textbf{21}, 26 (2015)}}].}

	\cvline{11/28/2014 \\ \textcolor{blue}{Talk}}
	{\textit{Local density waves of a two-dimensional gas of tilted dipoles}.
	\textbf{A.K. Fedorov}, I.L. Kurbakov, and Yu.E. Lozovik.
	57th Scientific Conference of the \textcolor{blue}{\href{http://mipt.ru/en/}{Moscow Institute of Physics and Technology}}, 
	Moscow, Russia.}

	\cvline{11/25/2014 \\ \textcolor{blue}{Talk}}
	{\textit{Tomographic discord of two-qubit states}.
	\textbf{A.K. Fedorov}, E.O. Kiktenko, O.V. Man'ko, and V.I. Man'ko.
	57th Scientific Conference of the \textcolor{blue}{\href{http://mipt.ru/en/}{Moscow Institute of Physics and Technology}}, 
	Moscow, Russia.}

	\cvline{07/15/2014 \\ \textcolor{blue}{Poster}}
	{\textit{Structural monitoring system with fiber Bragg grating sensors: Implementation and software solution}.
	\textbf{A.K. Fedorov}, V.A. Lazarev, I.P. Makhrov, N.O. Pozhar, M.N. Anufriev, A.B. Pnev, and V.E. Karasik.
	\textcolor{blue}{\href{http://www.lasphys.com/workshops/lasphys14/}{23rd International Laser Physics Workshop}},
	Sofia, Bulgaria 
	[\textcolor{blue}{\href{http://dx.doi.org/10.1088/1742-6596/594/1/012049}{Journal of Physics: Conference Series}} \textbf{594}, 012049 (2015), 
	{\textcolor{blue}{\href{http://arxiv.org/abs/1412.5838}{arXiv:1412.5838}}}].}
	
	\cvline{07/15/2014 \\ \textcolor{blue}{Talk}}
	{\textit{Tomographic measure of asymmetry in two-qubit states}.
	\textbf{A.K. Fedorov}, E.O. Kiktenko, O.V. Man'ko, and V.I. Man'ko.
	\textcolor{blue}{\href{http://www.lasphys.com/workshops/lasphys14/}{23rd International Laser Physics Workshop}},
	Sofia, Bulgaria
	[\textcolor{blue}{\href{http://dx.doi.org/10.1088/1742-6596/594/1/012045}{Journal of Physics: Conference Series}} \textbf{594}, 012045 (2015), 
	{\textcolor{blue}{\href{http://arxiv.org/abs/1412.5812}{arXiv:1412.5812}}}].}

	\cvline{07/07/2014 \\ \textcolor{blue}{Talk}}
	{\textit{Perturbation theory of observable linear systems and asymptotic control theory}.
	\textbf{A.K. Fedorov} and A.I. Ovseevich.
	\textcolor{blue}{\href{http://www.math.bas.bg/mds2014/}{International Conference ``Mathematics Days in Sofia''}},
	Sofia, Bulgaria.}	

	\cvline{06/17/2014 \\ \textcolor{red}{Invited talk}}
	{\textit{Generalized dry-friction-type control for a system of oscillators}.
	A.I. Ovseevich and \textbf{A.K. Fedorov}.
	\textcolor{blue}{\href{http://vspu2014.ipu.ru}{XII All-Russian Conference on Control Problems}},
	Moscow, Russia.}	

	\cvline{06/02/2014 \\ \textcolor{red}{Invited talk}}
	{\textit{Quantum cryptography: RQC project}.
	\textbf{A.K. Fedorov}. Digital security, personal data security, biometrics.
	\textcolor{blue}{\href{http://www.startupvillage.ru}{Startup Village}},
	Skolkovo, Moscow, Russia.}	

	\cvline{05/30/2014 \\ \textcolor{blue}{Poster}}
	{\textit{Roton-maxon spectrum and stability problem for dipolar atoms and excitons systems}.
	\textbf{A.K. Fedorov}, Y.E. Shchadilova, I.L. Kurbakov, and Yu.E. Lozovik.
	\textcolor{blue}{\href{http://www.mifp.eu/SCHOOLS/RQC-2014/}{International Conference on Problems of Strongly Correlated and Interacting Systems}},
	 St-Petersburg, Russia.}

	\cvline{04/15/2014 \\ \textcolor{red}{Invited talk}}
	{\textit{\textcolor{blue}{\href{http://www.mathnet.ru/php/presentation.phtml?option_lang=rus&presentid=8938}
	{From approximate reachable sets to asymptotic control theory}}}.
	\textbf{A.K. Fedorov} and A.I. Ovseevich.
	\textcolor{blue}{\href{http://gc2014.mi.ras.ru}{International Youth Conference ``Geometry \& Control''}},
	Moscow, Russia.}

	\cvline{04/14/2014 \\ \textcolor{blue}{Poster}}
	{\textit{Roton-maxon spectrum and stability problem for systems of dipolar bosonic particles}.
	\textbf{A.K. Fedorov}, Y.E. Shchadilova, I.L. Kurbakov, and Yu.E. Lozovik.
	\textcolor{blue}{\href{http://dynastyfdn.ru}{``Young Scientists of Russia'', Dynasty Foundation}},
	Moscow, Russia.}

	\cvline{03/23/2014 \\ \textcolor{blue}{Poster}}
	{\textit{Roton-maxon excitation spectrum for Q2D weakly interacting dipolar excitons}.
	\textbf{A.K. Fedorov}, I.L. Kurbakov, and Yu.E. Lozovik.
	\textcolor{blue}{\href{http://www.rqc.ru/events/?ELEMENT_ID=888}{APS March Meeting 2014}},
	Denver, Colorado, USA
	[\textcolor{blue}{\href{http://dx.doi.org/10.1088/1742-6596/414/1/012036}{Bulletin of the American Physical Society}}
	\textbf{59}, 1 (2014)].}

	\cvline{11/29/2013 \\ \textcolor{red}{Best talk}}
	{\textit{Roton instability of Q2D weakly interacted dipolar excitons}.
	\textbf{A.K. Fedorov}, I.L. Kurbakov, and Yu.E. Lozovik.
	56th Scientific Conference of the \textcolor{blue}{\href{http://mipt.ru/en/}{Moscow Institute of Physics and Technology}}, 
	Troitsk, Russia.}
	
	\cvline{10/29/2013 \\ \textcolor{red}{Invited talk}}
	{\textit{Quantum tomography: current state and perspectives}.
	\textbf{A.K. Fedorov}.
	Colloquium, 
	\textcolor{blue}{\href{http://fn.bmstu.ru/}{Faculty of Fundamental Science}},
	\textcolor{blue}{\href{http://fn.bmstu.ru/index.php/fn4}{Department of Physics}},
	\textcolor{blue}{\href{http://bmstu.ru/}{Bauman University}}, Moscow, Russia.}
	
	\cvline{10/29/2013 \\ \textcolor{red}{Invited talk}}
	{\textit{2D and 1D systems with the dipole-dipole interaction}.
	\textbf{A.K. Fedorov}.
	Colloquium, 
	\textcolor{blue}{\href{http://fn.bmstu.ru/}{Faculty of Fundamental Science}},
	\textcolor{blue}{\href{http://fn.bmstu.ru/index.php/fn4}{Department of Physics}},
	\textcolor{blue}{\href{http://bmstu.ru/}{Bauman University}}, Moscow, Russia.}
	
	\cvline{07/23/2013 \\ \textcolor{blue}{Poster}}
	{\textit{Feynman path integrals in quantum tomography}.
	\textbf{A.K. Fedorov}.
	\textcolor{blue}{\href{http://www.rqc.ru/events/?ELEMENT_ID=888}{The Second International Conference on Quantum Technologies}},
	Moscow.}
	
	\cvline{07/23/2013 \\ \textcolor{blue}{Poster}}
	{\textit{2D tilted dipoles: density waves vs. phonon collapse}.
	\textbf{A.K. Fedorov}, I.L. Kurbakov and Yu.E. Lozovik.
	\textcolor{blue}{\href{http://www.rqc.ru/events/?ELEMENT_ID=888}{The Second International Conference on Quantum Technologies}},
	Moscow.}	
	
	\cvline{06/11/2013 \\ \textcolor{red}{Invited talk}}
	{\textit{Asymptotically optimal feedback control for a system of linear oscillators} 
	({plenary}).
	\underline{A.I. Ovseevich}, and \textbf{A.K. Fedorov}.
	\textcolor{blue}{\href{http://www.tu-sofia.bg/eng_new/fpmi/amee/}{The 39th International Conference ``Application of Mathematics in Engineering and Economics''}}, Sozopol, Bulgaria
	[\textcolor{blue}{\href{http://dx.doi.org/10.1063/1.4854764}{{AIP Conference Proceedings}}} \textbf{1570}, 257 (2013)].}
	
	\cvline{06/06/2013 \\ \textcolor{blue}{Poster}}
	{\textit{\textcolor{blue}{\href{http://dx.doi.org/10.1088/1742-6596/486/1/012024}{Sensing of phase transition in medium with terahertz pulsed spectroscopy}}}.
	K.I. Zaytsev, I.N. Fokina, \textbf{A.K. Fedorov}, and S.O. Yurchenko.
	The 2nd Russia-Japan-USA Symposium on the Fundamental and Applied Problems of Terahertz Devices and Technologies, Moscow 
	[\textcolor{blue}{\href{http://dx.doi.org/10.1088/1742-6596/486/1/012024}{Journal of Physics: Conference Series \textbf{486}, 012024 (2014)}}].}
	
	\cvline{01/17/2013 \\ \textcolor{red}{Invited talk}}
	{\textit{Feedback control for a system of linear oscillators}.
	A.I. Ovseevich and \textbf{A.K. Fedorov}.
	Seminar ``Control theory and dynamics of systems'' of academician F.L. Cherous'ko,
	\textcolor{blue}{\href{http://www.ipmnet.ru/index_en.htm}{Institute for Problem in Mechanics RAS}},
	Moscow, Russia.}
	
	\cvline{11/23/2012 \\ \textcolor{red}{Best talk}}
	{\textit{Density wave supersolid in a two-dimensional gas of tilted dipoles}.
	\textbf{A.K. Fedorov}, I.L. Kurbakov, and Yu.E. Lozovik. 
	\textcolor{blue}{\href{http://mipt.ru/students/olympsaconfs/confmipt/f_5ykwxn/55conf//}{55th Scientific Conference of Moscow Institute of Physics and Technology}}, Troitsk, Russia}
	
	\cvline{11/15/2012 \\ \textcolor{red}{Invited talk}}
	{\textit{Quantum optics in the phase space}.
	\textbf{A.K. Fedorov}.
	Seminar of Optical Society of America Chapters ``Optics and Everything-Everything-Everything'', 
	Lomonosov Moscow State University, Moscow, Russia}
	
	\cvline{10/03/2012 \\ \textcolor{red}{Invited talk}}
	{\textit{Quantum cryptography: From Enigma to RSA and quantum computers}.
	\textbf{A.K. Fedorov}.
	Second Moscow Science Festival at the Bauman University.}
		
	\cvline{09/13/2012 \\ \textcolor{blue}{Talk}}
	{\textit{Phase delay distribution in dome lens antenna with displaced feed array}.
	\underline{V.I. Litun}, V.N. Mitrokhin, and \textbf{A.K. Fedorov}.
	22nd International Crimean Conference ``Microwave \& Telecommunication Technology'', Sevastopol, Ukraine
	[\textcolor{blue}{\href{http://ieeexplore.ieee.org/xpl/login.jsp?tp=&arnumber=6336056}{IEEE Proceedings Catalog Number CFP12788-PRT}}].}	
		
	\cvline{08/10/2012 \\ \textcolor{red}{Invited talk}}
	{\textit{Quantum tomograms and their application in quantum information science}.
	\textbf{A.K. Fedorov}.
	Quantum Lunch, Institute for Quantum Information Science, University of Calgary, Calgary, Canada.}
	
	\cvline{07/27/2012 \\ \textcolor{blue}{Talk}}
	{\textit{\textcolor{blue}{\href{http://dx.doi.org/10.1088/1742-6596/414/1/012040}{Quantum tomograms and their application in quantum information science}}}.
	\textbf{A.K. Fedorov}, S.O. Yurchenko, K.I. Zaytsev, and I.N. Fokina.
	\textcolor{blue}{\href{http://www.lasphys.com/workshops/lasphys12/}{21st International Laser Physics Workshop}}, Calgary, Canada
	[\textcolor{blue}{\href{http://dx.doi.org/10.1088/1742-6596/414/1/012040}{Journal of Physics: Conference Series \textbf{414}, 012040 (2013)}}].}
	
	\cvline{07/25/2012 \\ \textcolor{blue}{Poster}}
	{\textit{\textcolor{blue}{\href{http://dx.doi.org/10.1088/1742-6596/414/1/012036}{Roton instability and phonon collapse of two-dimensional tilted dipole atoms}}}.
	\textbf{A.K. Fedorov}, I.L. Kurbakov, and Yu.E. Lozovik.
	\textcolor{blue}{\href{http://www.lasphys.com/workshops/lasphys12/}{21st International Laser Physics Workshop}}, Calgary, Canada
	[\textcolor{blue}{\href{http://dx.doi.org/10.1088/1742-6596/414/1/012036}{Journal of Physics: Conference Series \textbf{414}, 012036 (2013)}}].}
	
	\cvline{04/09/2012 \\ \textcolor{blue}{Talk}}
	{\textit{Feynman path integrals for quantum tomograms}.
	\textbf{A.K. Fedorov}.
	Seminar of the group of Prof. O.G. Smolyanov,
	Department of Theory of Functions and Functional analysis, 
	Mathematics \& Mechanics Faculty, 
	Lomonosov Moscow State University, Moscow, Russia.}

	\cvline{02/06/2012 \\ \textcolor{blue}{Poster}}
	{Roton instability phenomena of two-dimensional tilted dipole system in a thin layer.
	\textbf{A.K. Fedorov}, Yu.E. Lozovik, and I.L. Kurbakov.
	Young Physicist Conference, Moscow, Russia
	[\textcolor{blue}{\href{http://konkmolphys.moomfo.ru/sites/default/files/1-2012_prilog.pdf}{Physics in High Education (Special Issue) \textbf{18}, 61 (2012)}}].}

	\cvline{11/25/2011 \\ \textcolor{red}{Best talk}}
	{\textit{Roton instability of two-dimensional tilted dipoles in a thin layer}.
	I.L. Kurbakov, Yu.E. Lozovik, and \textbf{A.K. Fedorov}.
	\textcolor{blue}{\href{http://mipt.ru/students/olympsaconfs/confmipt/f_5ykwxn/54conf.1/}{54th Scientific Conference of Moscow Institute of Physics and Technology}}, Troitsk, Russia.}
	
	\cvline{02/01/2011 \\ \textcolor{red}{Best poster}}
	{Tomographic approach to quantum mechanics.
	\textbf{A.K. Fedorov} and S.O. Yurchenko.
	Young Physicist Conference, Moscow, Russia
	[\textcolor{blue}{\href{http://konkmolphys.moomfo.ru/sites/default/files/1-2011_prilog.pdf}{Physics in High Education (Special Issue) \textbf{17}, 23 (2011)}}].}

	\cvline{01/26/2011 \\ \textcolor{blue}{Talk}}
	{\textit{Tomographic representation in quantum mechanics}.
	\textbf{A.K. Fedorov} and S.O. Yurchenko.
	The 6th Russian Scientific Conference ``Irreversible Processes in Nature and Technology'', 
	Moscow, Russia.}
	
	\cvline{06/01/2010 \\ \textcolor{blue}{Talk}}
	{\textit{Probability representation of quantum states: quantum tomography}.
	\textbf{A.K. Fedorov}.
	Colloquium, 
	\textcolor{blue}{\href{http://fn.bmstu.ru/}{Faculty of Fundamental Science}},
	\textcolor{blue}{\href{http://fn.bmstu.ru/index.php/fn4}{Department of Physics}},
	\textcolor{blue}{\href{http://bmstu.ru/}{Bauman University}}, Moscow, Russia.}
	
\iffalse
	
\section{Conference presentations of colloborators}

	\cvline{04/24/2013 \\ \textcolor{red}{Invited talk}}
	{\textit{Quantum physics for engineers}. 
	\textbf{A.K. Fedorov}.
	Conference Dedicated to the 50th anniversary  of the Evening Physics and Mathematics School at Bauman University, Bauman University.}

	
	\cvline{06/07/2013 \\ \textcolor{red}{Invited talk}}
	{\textit{Quantum information science}.
	\textbf{A.K. Fedorov}.
	Meeting of High School Students, Department of Computer Science \& Control Systems, Bauman University.}
	
	\cvline{25/05/2015 \\ \textcolor{blue}{Talk}}
	{\textit{Multilevel artificial atoms as two-qubit systems}.
	A.K. Fedorov, \textbf{E.O. Kiktenko}, and V.I. Man'ko.
	\textcolor{blue}{\href{http://qopt.org/seminardnk}{The Ninth Seminar Dedicated to the Memory of D.N. Klyshko}}, Moscow, Russia.}





	\cvline{07/14/2014}
	{\textit{Complete characterization of a multimode quantum black box}
	({invited}).
	I.A. Fedorov, A.K. Fedorov, \underline{Y.V. Kurochkin}, and A. I. Lvovsky.
	\textcolor{blue}{\href{http://www.lasphys.com/workshops/lasphys14/}{23rd International Laser Physics Workshop}},
	Sofia, Bulgaria.}
	
	\cvline{07/07/2014}
	{\textit{Foundations of asymptotic control theory for a system of linear oscillators}
	({invited}).
	A.K. Fedorov and \underline{A.I. Ovseevich}.
	\textcolor{blue}{\href{http://www.math.bas.bg/mds2014/}{International Conference ``Mathematics Days in Sofia''}},
	Sofia, Bulgaria.}
	
	\cvline{05/30/2014}
	{\textit{Multimode quantum black box characterization}
	({invited}).
	I.A. Fedorov, A.K. Fedorov, \underline{Y.V. Kurochkin}, and A.I. Lvovsky.
	\textcolor{blue}{\href{http://www.inrim.it/~brida/Quantum_2014/}{Quantum 2014 --- Workshop ad memoriam of Carlo Novero}},
	Torino, Italy.}
	
	\cvline{09/03/2013}
	{\textit{\textcolor{blue}{\href{http://itas2013.iitp.ru/en/session1.html}{Asymptotically optimal feedback control for a systems of linear oscillators}}}.
	A.K. Fedorov and \underline{A.I. Ovseevich}.
	\textcolor{blue}{\href{http://itas2013.iitp.ru/ru/index.html}{The 37th Conference for Young Scientists and Engineers ``Information Technology and Systems''}},
	Svetlogorsk.}
	
	\cvline{07/08/2013}
	{\textit{Asymptotically optimal feedback control for a system of linear oscillators} 
	({invited}).
	\underline{A.I. Ovseevich}, and A.K. Fedorov.
	\textcolor{blue}{\href{http://agora.guru.ru/display.php?conf=mctm2013}{The International Conference on Mathematical Control Theory and Mechanics}}, 
	Suzdal.}
	
\section{Seminars talks}

	\cvline{04/30/2014}{A.K. Fedorov. \textit{Quantum information technologies and their applications}, 
	Faculty of Informatics and Control Systems, 
	Department of Information Defense,
	\textcolor{blue}{\href{http://bmstu.ru/}{Bauman University}}
	(Head of the seminar is Prof. M.P. Sychev).}

	\cvline{03/22/2012}{A.K. Fedorov, \textit{Tomographic methods in quantum mechanics},
	\textcolor{blue}{\href{http://isan.troitsk.ru/en/div_lsn.php}{Laboratory of spectroscopy of nanostructures}},
	\textcolor{blue}{\href{http://isan.troitsk.ru/en/}{Institute for Spectroscopy RAS}}, 
	(Head of the seminar Prof. Yu.E. Lozovik).}
	
	\cvline{03/07/2012}{\textbf{A.K. Fedorov}, I.L. Kurbakov and Yu.E. Lozovik, \textit{Instability of two-dimensional tilted dipole in a thin layer: phonon collapse and density matter waves}, 
	\textcolor{blue}{\href{http://isan.troitsk.ru/en/div_lsn.php}{Laboratory of spectroscopy of nanostructures}},
	\textcolor{blue}{\href{http://isan.troitsk.ru/en/}{Institute for Spectroscopy RAS}}, 
	(Head of the seminar Prof. Yu.E. Lozovik).}
	
	\cvline{02/21/2012}{A.K. Fedorov, \textit{Tomographic representation of quantum mechanics}, 
	\textcolor{blue}{\href{http://photonics.bmstu.ru}{Research and Educational Center ``Photonics and Infrared Technology''}},
	\textcolor{blue}{\href{http://bmstu.ru/}{Bauman University}},
	(Head of the seminar is Dr. S.O. Yurchenko).}

\fi

			
\iffalse

	\cvline{06/01/2011}{A.K. Fedorov, \textit{Probability representation of quantum states: quantum tomography}, 
	\textcolor{blue}{\href{http://fn.bmstu.ru/}{Faculty of Fundamental Science}},
	\textcolor{blue}{\href{http://fn.bmstu.ru/index.php/fn4}{Department of Physics}},
	\textcolor{blue}{\href{http://bmstu.ru/}{Bauman University}},
	(Head of the seminar Prof. A.N. Morozov).}

	\cvline{04/10/2014}{\underline{I.A. Fedorov}, A.K. Fedorov, Y.V. Kurochkin, and A. I. Lvovsky. \textit{Tomography of multimode quantum processes}, 
	Scientific Seminar of G.S. Landsberg Optical Department, 
	Lebedev Physical Institute 
	(Head of the seminar is A.V. Masalov).}

	\cvline{02/23/2014}{\underline{A.I. Ovseevich}, A.K. Fedorov, \textit{Generalized dry-friction-type control for damping of a system of linear oscillators}, 
	Scientific Seminar on Control Theory and Dynamical Systems
	(Head of the seminar is academician F.L. Cherous'ko).}

\fi


\section{Teaching experience}

	\cventry{2013}{Teaching}{\textcolor{blue}{\href{http://icqt.org/events/kruzhok}{RQC quantum physics classes}} for high school students}{}{}{}

	\cventry{2012}{Teaching}{Lecture course ``Cryptography and steganography'',  \textcolor{blue}{\href{http://isot.bmstu.ru}{Bauman University}}}{}{}{}

	\cventry{2011 -- 2013}{Teaching}{Lecture course ``General physics'', \textcolor{blue}{\href{http://physmath.bmstu.ru}{Evening school at Bauman University}}}{}{}{}

	\cventry{2012 -- 2013}{Supervising}{co-supervisor in high school research projects at ``Step into the Future, Moscow''}{}{}{}
	

\section{Popular articles}

	\cvline{2014}
	{\textbf{A.K. Fedorov} and R.\,Y.\,Yunusov. 
	{\textcolor{blue}{\href{http://www.engineering.com/ElectronicsDesign/ElectronicsDesignArticles/ArticleID/8918/Beyond-the-Apple-Watch-How-Quantum-Sensors-will-Change-the-World.aspx}
	{How quantum sensors will change the world?}}}  //
	{\textcolor{blue}{\href{http://www.engineering.com/Electronics.aspx}{Engineering.com}}}.}

\section{References}

	\cventry{1.}
	{{\textcolor{blue}{\href{http://qis.ucalgary.ca/~lvov/}
	{Prof. G.V. Shlyapnikov}}}}{}{PhD advisor}
	{\newline LPTMS, University of Amsterdam, \& Russian Quantum Center}
	{\textcolor{blue}{\href{mailto:shlyapn@lptms.u-psud.fr}{shlyapn@lptms.u-psud.fr}}}{}

	\cventry{2.}
	{{\textcolor{blue}{\href{http://qis.ucalgary.ca/~lvov/}
	{Prof. A.I. Lvovsky}}}}{}{RQC Fellowship advisor}
	{\newline University of Calgary \& Russian Quantum Center}
	{\textcolor{blue}{\href{mailto:lvov@ucaglary.ca}{lvov@ucaglary.ca}}}{}
	
	\cventry{3.}
	{{\textcolor{blue}{\href{http://isan.troitsk.ru/ru/div_lsn.php}
	{Prof. Yu.E. Lozovik}}}}{}{Frequent collaborator}
	{\newline Institute for Spectroscopy RAS}
	{\textcolor{blue}{\href{mailto:lozovik@isan.troitsk.ru}{lozovik@isan.troitsk.ru}}}{}	
	
	\cventry{4.}
	{{\textcolor{blue}{\href{}
	{Prof. V.I. Man'ko}}}}{}{Frequent collaborator}
	{\newline P.N. Lebedev Physical Institue RAS}
	{\textcolor{blue}{\href{mailto:manko@lebedev.ru}{manko@lebedev.ru}}}
	
	\cventry{5.}
	{{\textcolor{blue}{\href{http://www.ipmnet.ru/lab02/Ovseevich.htm}
	{Prof. A.I. Ovseevich}}}}{}{Undergraduate studies supervisor}
	{\newline Institute for Problem in Mechanics RAS}
	{\textcolor{blue}{\href{mailto:ovseev@ipmnet.ru}{ovseev@ipmnet.ru}}}
	
%	\cventry{5.}	
%	{{\textcolor{blue}{\href{http://teratech.ru/en/}
%	{Prof. S.O. Yurchenko}}}}{}{Undergraduate studies supervisor}
%	{\newline Bauman University, Department of Physics}
%	{\textcolor{blue}{\href{mailto:st.yurchenko@bmstu.ru}{st.yurchenko@bmstu.ru}}}{}

%	\cventry{6.}	
%	{{\textcolor{blue}{\href{http://www.bmstu.ru/ps/~yanabutko/}
%	{Dr. Ya.A. Kinderkneht}}}}{}{Associated professor, lecturer}
%	{\newline Bauman University, Department of Mathematical Simulation}
%	{\textcolor{blue}{\href{mailto:yanabutko@yandex.ru}{yanabutko@yandex.ru}}}{}

\end{document}