\documentclass[10pt,a4paper,sans]{moderncv}
\usepackage[utf8]{inputenc}
\moderncvstyle{classic}
\moderncvcolor{blue}
\usepackage[scale=0.87]{geometry}
\setlength{\hintscolumnwidth}{2.5cm}
\usepackage{amsfonts,amssymb}
\usepackage{amsmath}

\firstname{Aleksey}
\familyname{Fedorov}
\address{Mitrofanova street, 23,}{Moscow Region, Lubertsy}
\phone{+7 (916) 297-09-77}
\email{lex1026@gmail.com}
\renewcommand\refname{Selected publications}
\nopagenumbers{}

\begin{document}

\begin{center}
\Large
\textcolor{blue}{Aleksey Fedorov}
\end{center}

\section{Biography}

Aleksey Fedorov graduated from the school at the age of 15 and became a student of the Bauman Moscow State Technical University. 
For excellent academic achievements he awarded by number of scholarships such as Russian Federation Government Scholarship (2013-2014), 
Russian President Scholarship (2014-2015), Bauman University Scientific Committee Scholarship (2014), and Bauman University Alumni Club Scholarship (2015). 
He was graduated (with honours) from the Bauman Moscow State Technical University in 2015.

\medskip

Starting from the first year of studies in the university, Aleksey was involved in research projects of several groups including groups of Prof. Y.E. Lozovik at the Institute of Spectroscopy RAS, 
Prof. A.I. Ovseevich at the Institute for Problem in Mechanics RAS, and Prof. V.I. Man'ko at the Lebedev Physical Institute. 
After summer internship in the group of Prof. A.I. Lvovsky in the University of Calgary, he became a first member of the A.I. Lvovsky's group at the Russian Quantum Center (RQC). 
He combined research work with organisation of the experimental laboratory in the RQC.
His research activity was awarded by the RQC fellowship for undergraduate students (2013-2015) and the Dynasty Foundation Fellowship for undergraduate students (2014-2015).
In the framework of the RQC fellowship,
Aleksey shared his time between quantum optics and quantum communications projects in the group of Prof. A.I. Lvovsky  and many-body theory in the group of Prof. G.V. Shlyapnikov. 

\medskip

Aleksey has 14 papers published in peer-reviewed journals and more than 10 invited talks on international meetings. 
He is a reviewer for a number of physics journals.
The Moscow Physical Society three times awarded his works on the young physics conferences. 
He was also awarded by the New Generation Award at the XV National forum for information security ``INFOFORUM 2013''.

\medskip

Now Aleksey is a PhD Student under supervision of Prof. G.V. Shlyapnikov in the Laboratory of Theoretical Physics and Statistical Models at the University Paris-Sud 
and Junior Researcher in the Many-body Theory Group at the Russian Quantum Center. 
PhD defence of his thesis is scheduled on the beginning of 2017. 

\section{Research experience}

	\cventry{Sept'15 -- present}
	{CNRS PhD Student}{{\textcolor{blue}{\href{https://www.universite-paris-saclay.fr/en/}{Universit{\' e} Paris-Saclay}}},
	\textcolor{blue}{\href{http://lptms.u-psud.fr/en}{Laboratoire de Physique Th{\'e}orique et Mod{\`e}les Statistique, CNRS \& Universit{\' e} Paris Sud XI}}}
	{\textit{Supervisor}: Prof. \textcolor{blue}{\href{http://staff.science.uva.nl/~walraven/shlyapnikov/GoraShlyapnikov-french.htm}{Georgy Shlyapnikov}},
	{\textit{Tutor}: Prof. \textcolor{blue}{\href{http://lptms.u-psud.fr/membres/groux/}{Guillaume Roux}}}}{}{}{}{}


	\cventry{Oct'12 -- present}
	{BSc Student/RQC Student Fellow/Junior Researcher}
	{\textcolor{blue}{\href{http://rqc.ru}{Russian Quantum Center}}}
	{\textcolor{blue}{\href{http://www.rqc.ru/groups/lvovsky/}{Quantum Optics}} \& 
	\textcolor{blue}{\href{http://www.rqc.ru/groups/shlyapnikov/}{Many-body Theory}}}
	{\textit{Supervisor}: \textcolor{blue}{\href{http://www.rqc.ru/members/georgy.shlyapnikov/}{Prof. Georgy Shlyapnikov}},
	{\textit{Point of Contact}: \textcolor{blue}{\href{http://www.rqc.ru/members/alexander.lvovsky/}{Prof. Alexander Lvovsky}}}}{}                                            
	
	\cventry{Oct'12 -- Jul'13\,\,}
	{BSc Student}
	{\textcolor{blue}{\href{http://fn.bmstu.ru/index.php/fn4}{Department of Physics}}, \textcolor{blue}{\textcolor{blue}{\href{http://bmstu.ru}{Bauman University}}}}
	{\newline \textcolor{blue}{\href{http://teratech.ru/en}{Condensed Matter Theory}}}
	{\textit{Supervisor}: \textcolor{blue}{\href{http://teratech.ru/en/peoples}{Dr. Stanislav Yurchenko}}}{}

	\cventry{Dec'10 -- Jun'14}
	{BSc Student}
	{\textcolor{blue}{\href{http://www.ipmnet.ru}{Institute for Problem in Mechanics, Russian Academy of Sciences}}}
	{\newline \textcolor{blue}{\href{http://www.ipmnet.ru/lab02.htm}{Mechanics of Controlled Systems}}}
	{\textit{Supervisor}: \textcolor{blue}{\href{http://www.ipmnet.ru/lab02/Ovseevich.htm}{Dr. Alexander Ovseevich}}}{}
	
\section{Research visits}

	\cventry{Dec'13 -- Jan'14}
	{Visiting Scholar}
	{\textcolor{blue}{\href{http://physics.harvard.edu}{Department of Physics}}, \textcolor{blue}{\href{http://www.harvard.edu}{Harvard University}}}
	{\newline \textcolor{blue}{\href{http://cmt.harvard.edu}{Condensed Matter Theory}}}
	{\textit{Supervisor}: \textcolor{blue}{\href{http://cmt.harvard.edu/demler/}{Prof. Eugene Demler}}}{}        

	\cventry{Jul'12 -- Aug'12\,}
	{Visiting Research Associate}
	{\textcolor{blue}{\href{http://phas.ucalgary.ca}{Department of Physics and Astronomy}}, \textcolor{blue}{\href{http://www.ucalgary.ca}{University of Calgary}}}
	{\newline \textcolor{blue}{\href{http://www.iqst.ca}{Institute for Quantum Science and Technology}}}
	{\textit{Supervisor}: \textcolor{blue}{\href{http://www.rqc.ru/members/alexander.lvovsky/}{Prof. Alexander Lvovsky}}}{}	

\end{document}